Paper 2 !DRAFT! Do not circulate!

### 2015-01-01 Articles/Article_EcolEcon_2014/Paper2.Rnw
Explanatory note.
Moved text for spaghetti graphs.
Minor edits.

The fraction of GDP growth explained by the Solow residual~($f$)
can be given as
%
\begin{equation} \label{eq:frac_growth_explained_by_solow}
  f \equiv \frac{\lambda}{\frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t}} 
            = 1 - \frac{\alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
                      + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
                      + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t}}
                  {\frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t}} \; .
\end{equation}
%
Using forward differences to estimate $f$ yields
%
\begin{equation} \label{eq:f_finite_diff_1}
  f_{i,j} = \frac{\lambda_{i,j}}{\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}}
       = 1 - \frac{\alpha \frac{1}{k_i}\frac{k_j - k_i}{t_j - t_i} 
            + \beta \frac{1}{l_i}\frac{l_j - l_i}{t_j - t_i} 
            + (1 - \alpha - \beta) \frac{1}{e_i}\frac{e_j - e_i}{t_j - t_i} }
            {\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}} \; .
\end{equation}
%
Simplifying slightly gives
%
\begin{equation} \label{eq:f_finite_diff_2}
  f_{i,j} = 1 - \frac{\alpha \left( \frac{k_j}{k_i} - 1 \right) 
                      + \beta \left( \frac{l_j}{l_i} - 1 \right)
                      + (1 - \alpha - \beta) \left( \frac{e_j}{e_i} - 1 \right)}
            {\left( \frac{y_j}{y_i} - 1 \right)} \; ,
\end{equation}
%
which is an estimate to the instantaneous value of $f$ 
given by Equation~\ref{eq:frac_growth_explained_by_solow}.

@@

We can also estimate values for 
the fraction of economic growth explained by the Solow residual ($f$)
by $f_{ij}$
with $i$ and $j$ in Equation~\ref{eq:f_finite_diff_2} separated by \Sexpr{lag} years.
The results are shown in Figure~\ref{fig:CD_solowPerc_time_series}.

>>>>

The fraction~($f$) of GDP growth explained by the Solow residual
can be given as
%
\begin{equation} \label{eq:frac_growth_explained_by_solow}
  f \equiv \frac{\lambda}{\frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t}} 
            = 1 - \frac{\alpha \frac{1}{k}\frac{\mathrm{d}k}{\mathrm{d}t} 
                      + \beta \frac{1}{l}\frac{\mathrm{d}l}{\mathrm{d}t} 
                      + (1 - \alpha - \beta) \frac{1}{e}\frac{\mathrm{d}e}{\mathrm{d}t}}
                  {\frac{1}{y}\frac{\mathrm{d}y}{\mathrm{d}t}} \; .
\end{equation}
%
Using forward differences to estimate $f$ yields
%
\begin{equation} \label{eq:f_finite_diff_1}
  f_{i,j} = \frac{\lambda_{i,j}}{\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}}
       = 1 - \frac{\alpha \frac{1}{k_i}\frac{k_j - k_i}{t_j - t_i} 
            + \beta \frac{1}{l_i}\frac{l_j - l_i}{t_j - t_i} 
            + (1 - \alpha - \beta) \frac{1}{e_i}\frac{e_j - e_i}{t_j - t_i} }
            {\frac{1}{y_i}\frac{y_j - y_i}{t_j - t_i}} \; .
\end{equation}
%
Simplifying by cancelling $t_j - t_i$ terms and simplifying gives
%
\begin{equation} \label{eq:f_finite_diff_2}
  f_{i,j} = 1 - \frac{\alpha \left( \frac{k_j}{k_i} - 1 \right) 
                      + \beta \left( \frac{l_j}{l_i} - 1 \right)
                      + (1 - \alpha - \beta) \left( \frac{e_j}{e_i} - 1 \right)}
            {\left( \frac{y_j}{y_i} - 1 \right)} \; ,
\end{equation}
%
which is an estimate of the instantaneous value of $f$ 
given by Equation~\ref{eq:frac_growth_explained_by_solow}.

@@

We can also estimate values for 
the fraction~($f$) of economic growth explained by the Solow residual
by $f_{ij}$
with $i$ and $j$ in Equation~\ref{eq:f_finite_diff_2} separated by \Sexpr{lag} years.
The results are shown in Figure~\ref{fig:CD_solowPerc_time_series}. 
Note that data spanning year~$i$--year~$j$ is plotted at year~$i$ in 
Figures~\ref{fig:CD_lambda_time_series} and~\ref{fig:CD_solow_Perc_time_series}.
